CTest Integration of Sikuli Automated GUI Testing

### 2011-06-21 Documentation/Article.tex
minor edit
to be submitted

\begin{abstract}
\noindent

\end{abstract}

@@

GUI testing is a key aspect of software development. Having a well defined
testing protocol is very important in maintaining a productive flow, especially
on the eve of a new release. As the software becomes more complex, testing each
feature can be immensely time consuming. We collected a list of over 400
different GUI tests for the GoFigure2 software~\cite{GoFigure2:Website} which
involved endlessly repetitive clicking and checking. This task took around 5
hours to complete each time a new release was ready. And debugging would push
release dates back days or even weeks. We decided to tackle this problem by
utilizing a new scripting language called
Sikuli~\cite{Sikuli:Documentation,Sikuli:Website,Yeh:2009:Sikuli} that can
automate any visual operation. In this way we could write scripts to automate
the GUI testing. This cut the time to complete each test drastically.
Furthermore, we have integrated the automated tests with CTest. Therefore we
are able to run the collection of tests every night and find bugs as they
arise instead of the night before a new release. As a result, the rate of new
releases increased drastically.\\

@@

In the \emph{Sikuli IDE}, the user can write scripts that include screenshot
thumbnails so they can visually track the functions of their code. The most
useful functions from Sikuli scripts are conveniently found as
buttons on the IDE. When using the IDE, Sikuli then saves a script in a
directory with a unique extension .sikuli. The directory consists of a python
script file (script file to be used by sikuli), an html file, and a list of all
the screenshot images used in the script.

@@

# here we add a sikuli test
add_sikuli_test( GoFigure2ToolbarTest toolbar.sikuli )
\end{verbatim}

@@

% ------------------------------------------------------------------------
\section{Conclusion}
\label{sec:Conclusion}

>>>>

\begin{abstract}
\noindent
In order to test our software GoFigure2~\cite{GoFigure2:Website} (for the
visualization and the processing of extremely large $3D+t$ microscopy images),
we utilized the visual programming technology Sikuli~\cite{Sikuli:Website} to
automate our GUI testing. We then integrated these Sikuli tests into CTest and
used CDash to report the results on a dashboard with the view to test our
software automatically every night and detect bugs as soon as they occur.  Our
rate of releases more than doubled as a result.
\end{abstract}

@@

GUI testing is a key aspect of software development. Having a well defined
testing protocol is very important in maintaining a productive flow, especially
on the eve of a new release. As the software becomes more complex, testing each
feature can be immensely time consuming. We collected a list of over 400
different GUI tests for the GoFigure2 software~\cite{GoFigure2:Website} which
involved endlessly repetitive clicking and checking. This task took around 5
hours to complete each time a new release was ready. And debugging would push
release dates back days or even weeks. We decided to tackle this problem by
utilizing a new scripting language called
Sikuli~\cite{Sikuli:Documentation,Sikuli:Website,Yeh:2009:Sikuli} that can
automate any visual operation. In this way we could write scripts to automate
the GUI testing. This cut the time to complete each test drastically.
Furthermore, we have integrated the automated tests with CTest. Therefore we
are able to run the collection of tests every night and find bugs as they
arise instead of the night before a new release. As a result, the rate of new
releases increased drastically from one
release every five months to one release every two months. \\

@@

In the \emph{Sikuli IDE}, the user can write scripts that include screenshot
thumbnails so they can visually track the functions of their code. The most
useful functions from Sikuli scripts are conveniently found as
buttons on the IDE. When using the IDE, Sikuli then saves a script in a
directory with a unique extension .Sikuli. The directory consists of a python
script file (script file to be used by Sikuli), an html file, and a list of all
the screenshot images used in the script.

@@

# here we add a Sikuli test
add_Sikuli_test( GoFigure2ToolbarTest toolbar.Sikuli )
\end{verbatim}

@@

% ------------------------------------------------------------------------
\section{Conclusion}
\label{sec:Conclusion}
In this paper we discussed the uses of Sikuli unit testing and how they can be
integrated into CTest.  Although we have recognized limitations within the
current infrastructure (Sikuli and CDash), there is great potential to make
these technologies more universal thanks to the fast growing Sikuli
community. The results of our increased productivity have proven this
technology well worth the effort.\\

Due to the previous exposed limitations (see section~\ref{sec:Limitations}),
provided examples may not run on your machine. However, it is easy enough to
adapt these tests to your system.

\section*{Note}
As of now, Sikuli has been successfully integrated with CTest on
linux, and it
requires some more work for Windows and Mac. We would welcome
contributions to make it happen!
